%-------------------------
% Resume in Latex
% Author : Sohail Mahmud
% Website: https://sohailmahmud.github.io/
% License : MIT
%------------------------

\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \vspace{-1pt}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sohailmahmud.com/}{\LARGE Mitul Savani}} & \href{https://sohailmahmud.com/}{Portfolio: \textbf{sohailmahmud.com}}\\ 
  {Folsom, CA} & {\href{https://github.com/sohailmahmud}{github.com/\textbf{sohailmahmud}}} \\
  {} & \href{mailto:sohailmahmud@outlook.com}{sohailmahmud@outlook.com}
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    
     \resumeSubheading
      {Software Developer (Mobile)}{Folsom, CA}
      {AgreeYa Solutions}{Aug. 2020 - Present}
      \resumeItemListStart
      \resumeItem{}
          {Working experience in the design and development of both greenfield and brownfield mobile applications across various platforms using hybrid technologies such as Flutter, Ionic, React Native.}
        \resumeItem{}
          {Developed many Proof-of-Concepts (POC's) to showcase new features in mobile application development to clients.}
        \resumeItem{}
          {Collaborated with DevOps team to design a scalable modular framework for continuous integration and automation of build generation, test case execution, and sending deliverables to the client.}
        \resumeItem{}
          {Working directly with Director and Enterprise Architect to consistently deliver high performance, maintainable, and reliable infrastructure on our client projects.}
        \resumeItem{}
          {Worked on estimates for project development and interacted with a client for the daily status call to identify key requirements, define project scope, develop a project plan and schedule.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Engineer}{Remote}
      {Kandou}{Nov. 2019 - Jul. 2020}
      \resumeItemListStart
        \resumeItem{}
          {Worked on setting up the core infrastructure of the mobile app such as Navigation flow, State Management using Redux, Authentication, Custom Components \& Styling, and designing user interaction screens.}
        \resumeItem{}
          {Responsible for beta testing build versions on TestFlight and releasing them to 500+ active users on app stores.}
        \resumeItem{}
          {Working in an agile environment consisting of analyzing users and peer feedback on the submitted work.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Development Intern \& Undergraduate Researcher}{San Francisco, CA}
      {Claryty | Bioinformatics Research Project by Stanford University}{Nov. 2018 - Oct. 2019}
      \resumeItemListStart
        \resumeItem{}
          {Developed a new pharmaceutical mobile application using React Native/Redux for consumers that presents adverse effect reports for prescription drugs.}
        \resumeItem{}
          {Involved in designing the architecture of software stack in order to scale future Food and Drug Administration(FDA) data sets and user input.}
        \resumeItem{}
          {Won 3rd prize out of 240 projects at the College of Science and Engineering annual showcase in 2019 at SF State.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Open Source Contributor}{}
      {Facebook | React Native Core, React Native Website}{}
      \resumeItemListStart
        \resumeItem{}
          {Updated API and Component docs to reflect the props and methods reflected in core repository(v62).}
          \resumeItem{}
          {Added 50+ libraries associated with UI, Analytic, Geo location, Deep Link, and Other Platforms to the RN directory.}
        \resumeItem{}
          {Contributed in migrating ImageStore native module into the new TurboModule System architecture of the repository(v59).}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
  
%-----------LEADERSHIP ACTIVITIES-----------------
\section{Leadership Activities}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Founder  - Tutoring Services}{San Francisco, CA}
      {Association of Computing Machinery at SF State}{Aug. 2017 - May. 2020}
      \resumeItemListStart
        \resumeItem{}
          {Improved overall academic performance of incoming freshmen and sophomores by 30\% in core courses such as Programming Methodology and Software Development by showing them effective use of standard data structures and complex algorithms.}
        \resumeItem{}
          {Recruited, organized, and trained tutors to sustain the services for the Computer Science Department.}
      \resumeItemListEnd
      
    % \resumeSubheading
    %   {Hackathon Organizer}{San Francisco, CA}
    %   {SF Hacks}{Nov. 2017 - May. 2020}
    %   \resumeItemListStart
    %     \resumeItem{}
    %       {Arranged first collegiate Hackathon in San Francisco with over 350 attendees.}
    %     \resumeItem{}
    %       {Spearhead an outreach team to reach out to 30+ companies for partnership and raised \$18,000 in sponsorship.}
    %   \resumeItemListEnd
      
      \resumeSubheading
      {Teaching Assistant}{San Francisco, CA}
      {MobileSpace | React Native Bootcamp}{Feb. 2018 - Apr. 2018}
      \resumeItemListStart
        \resumeItem{}
          {Took initiative in learning hybrid development and went on to successfully develop 2 functional apps under minimal supervision.}
        \resumeItem{}
          {Facilitated a dynamic and collaborative classroom of 15 students and conducted weekly office hours for further assistance.}
      \resumeItemListEnd

   \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Francisco State University}{\textit{Jan. 2016 - May. 2020}}
      {Bachelor's of Science in Computer Science}{GPA 3.82}
      \resumeItemListStart
        \resumeItem{Coursework: }
          {Hybrid Mobile Application Development | Human-Computer Interaction | Database System Design | Internet Application Design \& Development | Programming Methodology | Data Structures \& Analysis of Algorithms}
      \resumeItem{Dean's Scholar List: }
          {Spring 2018, Spring \& Fall 2017, Spring \& Fall 2016}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Programming Languages:}{ JavaScript, TypeScript, Java, Dart, C++, HTML/CSS}
    }
    \item{
     \textbf{Frameworks:}{ Flutter, React, React Native, Ionic, Redux, Node.js, Express.js}
    }
    \item{
     \textbf{Databases and Infrastructure:}{ AWS, Google Cloud Platform(GCP), Firebase, MySQL, PostgreSQL}
    }
     \item{
     \textbf{Tools \& Miscellaneous:}{ Visual Studio Code, XCode, Android Studio, REST API, Docker, Postman, Chrome Developer Tools, Git, NPM, Yarn, Jira, Trello, Notion}
    }
 \resumeSubHeadingListEnd
 

\end{document}